Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s07_problempinning.tex
Added citations

\section{Application: Finding completions of under-constrained glassy structures to isostatic}
\label{sec:bodypin}
% \bibliography{paper}

@@

\begin{definition}
\label{def:body-pin}
    A body-pin graph is a body-hyperpin graph with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin graph can also be seen as a \dfn{body-bar graph} where the bodies are the original bodies and each pin represents 2 bars from one body to another. Such body-bar graphs with 1 and 2-dof can be characterized by being $(3,4)$ and $(3,5)$-tight respectively.
\end{definition}

\begin{definition}
    A \dfn{multi-triangle-pin graph} is a body-hyperpin graph where each body is a triangle, meaning it is pinned in at most 3 places. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hyper-graphs, 1 and 2-dof can be characterized by $(2,4)$ and $(2,5)$-tightness respectively.
\end{definition}

@@

\begin{remark}
\label{rem:1dofcanon}

    All $(k,l)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar and joint graphs discussed in Section \ref{sec:DRP}. This is due tot he fact that such $(k,l)$-tight graphs are matroidal and have a pebble game.
\end{remark}

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}

\end{figure*}

@@

    Now if we want to minimize the algebraic complexity, we need to minimize the maximum $np(v)$ for any node $v$. In this case, we cannot always just choose the node furthest down the tree to pin because it could have many children. SO we will have to try pinning all nodes to see which gives the lowest algebraic complexity. This is still quadratic for the 1-dof case.

@@

\begin{openproblem}
    What is the complexity of the optimal completion problem when there are more than 2-dof. For higher number of dofs, the $(k,l)$ characterization is no longer matroidal.
\end{openproblem}

>>>>

\section{Application: Finding completions of under-constrained glassy structures to isostatic}
\label{sec:bodypin}
\bibliography{paper}

@@

\begin{definition}
\label{def:body-pin}
    A body-pin graph is a body-hyperpin graph with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin graph can also be seen as a \dfn{body-bar graph} where the bodies are the original bodies and each pin represents 2 bars from one body to another. Such body-bar graphs with 1 and 2-dof can be characterized by being $(3,4)$ and $(3,5)$-tight respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}.
\end{definition}

\begin{definition}
    A \dfn{multi-triangle-pin graph} is a body-hyperpin graph where each body is a triangle, meaning it is pinned in at most 3 places. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hyper-graphs, 1 and 2-dof can be characterized by $(2,4)$ and $(2,5)$-tightness respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}.
\end{definition}

@@

\begin{remark}\label{rem:1dofcanon}
    All $(k,l)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar and joint graphs discussed in Section \ref{sec:DRP}. This is due to the fact that such $(k,l)$-tight graphs are matroidal and have a pebble game, shown in \cite{Lee:2007:PGA}.
\end{remark}

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
%
\end{figure*}

@@

    Now if we want to minimize the algebraic complexity, we need to minimize the maximum $np(v)$ for any node $v$. In this case, we cannot always just choose the node furthest down the tree to pin because it could have many children. So we will have to try pinning all nodes to see which gives the lowest algebraic complexity. This is still quadratic for the 1-dof case.

@@

\begin{openproblem}
    What is the complexity of the optimal completion problem when there are more than 2-dof. For higher number of dofs, the $(k,l)$ characterization is no longer matroidal \cite{Lee:2007:PGA}.
\end{openproblem}
